---
output:
  html_document:
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
    fig_width: 7
    fig_height: 6
---


<style type="text/css">
div.main-container {
  max-width: 2000px;
  margin-left: auto;
  margin-right: auto;
}
</style>
<style>
.tocify {
color: black;
}
<!-- } -->
<!-- .tocify .tocify-header { -->
<!--     position: fixed; -->
<!--     <!-- top: 50px; --> -->
<!--     left: 50px; -->
<!--     width: 350px; -->
<!--     <!-- border: solid 3px black; --> -->
<!--     <!-- height: 200px; --> -->
<!--  border: none; -->
<!-- } -->
.tocify .tocify-header .active {
color: white;
background: #d80b8c;
font-weight: bold;
}
<!-- .tocify .tocify-item { -->
<!-- background: white; -->
<!-- color: black; -->
<!--  border: none; -->
<!-- } -->
</style>
<style>
  .nav-pills>li>a:hover, .nav-pills>li>a:focus, .nav-pills>li.active>a,     .nav-pills>li.active>a:hover, .nav-pills>li.active>a:focus{
     background-color: #212070;
     }
</style>
<style>
.container { width: 1800px; }
h2 {
  background-color: #dddedd;
  color: black;
  text-indent: 20px;
  <!-- font-weight: bold; -->
}
h3 {
  background-color: #f2f2f2;
  color: black;
  text-indent: 20px;
  <!-- font-weight: bold; -->
}
h4 {
  <!-- background-color: #dddedd; -->
  <!-- color: black; -->
  text-indent: 50px;
  <!-- font-weight: bold; -->
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```


```{r Load Packages, echo = FALSE, warning = FALSE, message = FALSE}

# # Load packages -----------------------------------------------------------------------------------
suppressMessages({
  memory.limit(size = 8000000)
  library(readxl)
  library(writexl)
  library(plyr)
  library(dplyr)
  library(data.table)
  library(zoo)
  library(shiny)
  library(shinydashboard)
  library(shinydashboardPlus)
  library(shinyWidgets)
  library(htmlwidgets)
  library(lubridate)
  library(tcltk)
  library(tidyverse)
  library(plotly)
  library(knitr)
  library(kableExtra)
  library(leaflet)
  library(grid)
  library(gridExtra)
  library(eeptools)
  library(ggQC)
  library(zipcodeR)
  library(utils)
  library(scales)
  library(chron)
  library(bupaR)
  library(shiny)
  library(DT)
  library(DiagrammeR)
  library(shinyalert)
  library(edeaR)
  library(processmapR)
  library(processmonitR)
  library(processanimateR)
  library(tidyr)
  library(lubridate)
  library(RColorBrewer)
  library(DiagrammeR)
  library(ggplot2)
  library(leaflet)
  library(readr)
  library(highcharter)
  library(ggforce) # for 'geom_arc_bar'
  library(packcircles) # for packed circle graph
  library(viridis)
  library(ggiraph)
  library(treemapify)
  library(treemap)
  library(broom)
  library(extrafont)
  library(tis) # for US holidays
  library(vroom)
  library(sjmisc)
  library(tools)
  library(here)
  library(shinyBS)
  library(shinyscreenshot)
  library(fasttime)
  library(shinycssloaders)
  library(feather)
  # library(zipcodeR)
  library(formattable)
  library(shinyjs)
  library(janitor)
  library(patchwork)
  library(flexdashboard)
  # library(tidyverse)
  # library(viridis)
  # library(hrbrthemes)
  # library(plotly)
  # install.packages("bsts")
  library(bsts)
  library(reactable)
  # install.packages("reactablefmtr")
  library(reactablefmtr)
  library(svDialogs)
  # library(openxlsx)
  library(flextable)
  library(officedown)
  library(officer)
  library(magrittr)
  library(webshot) 
  library(png)
  library(ggh4x)
  library(RODBC)
  library(DBI)
  library(odbc)
  library(dbplyr)
  library(pool)
  library(emojifont)
})


```


```{r Graph asthetics, echo = FALSE, warning = FALSE, message = FALSE}
### Color Functions for Graphs ============================================================

# Mount Sinai corporate colors "USE THIS TO ADD COLORS"
MountSinai_colors <- c(
  `dark purple`  = "#212070",
  `dark pink`    = "#d80b8c",
  `dark blue`    = "#00aeef",
  `dark grey`    = "#7f7f7f",
  `yellow`       = "#ffc000",
  `purple`       = "#7030a0",
  `med purple`   = "#5753d0",
  `med pink`     = "#f75dbe",
  `med blue`     = "#5cd3ff",
  `med grey`     = "#a5a7a5",
  `light purple` = "#c7c6ef",
  `light pink`   = "#fcc9e9",
  `light blue`   = "#c9f0ff",
  `light grey`   = "#dddedd"
  )

# Function to extract Mount Sinai colors as hex codes
# Use Character names of MountSinai_colors

MountSinai_cols <- function(...) {
  cols <- c(...)
  
  if (is.null(cols))
    return (MountSinai_colors)
  
  MountSinai_colors[cols]
}

# Color Function that can be used to call all colors is "MountSinai_cols()"
# Use in ggplot 

  #MountSinai_cols()       # will provide all colors and their hex codes in a table 
  #MountSinai_cols("pink") # will provide color name and the hex code for the pink color

# Create palettes 
MountSinai_palettes <- list(
  `all`   = MountSinai_cols("dark purple","dark pink","dark blue","dark grey",
                            "med purple","med pink","med blue","med grey", 
                            "light purple","light pink","light blue","light grey"),
  
  `main`  = MountSinai_cols("dark purple","dark pink","dark blue","dark grey"),
  
  `purple`  = MountSinai_cols("dark purple","med purple","light purple"),
  
  `pink`  = MountSinai_cols("dark pink","med pink","light pink"),
  
  `blue`  = MountSinai_cols("dark blue", "med blue", "light blue"),
  
  `grey`  = MountSinai_cols("dark grey", "med grey", "light grey"),
  
  `purpleGrey` = MountSinai_cols("dark purple", "dark grey"),
  
  `pinkBlue` = MountSinai_cols("dark pink", "dark blue")
  
)

# MountSinai_palettes
# Return function to interpolate a Mount Sinai color palette
# default value is the main palette, reverse = True will change the order

MountSinai_pal <- function(palette = "all", reverse = FALSE, ...) {
  pal <- MountSinai_palettes[[palette]]
  
  if (reverse) pal <- rev(pal)
  
  colorRampPalette(pal, ...)
}



# Scale Function for ggplot can be used instead of scale_color_manual
scale_color_MountSinai <- function(palette = "all", discrete = TRUE, reverse = FALSE, ...) {
  pal <- MountSinai_pal(palette = palette, reverse = reverse)
  
  if (discrete) {
    discrete_scale("colour", paste0("MountSinai_", palette), palette = pal, ...)
  } else {
    scale_color_gradientn(colours = pal(256), ...)
  }
}

# Scale Fill for ggplot insetead of scale_fill_manual 
scale_fill_MountSinai <- function(palette = "all", discrete = TRUE, reverse = FALSE, ...) {
  pal <- MountSinai_pal(palette = palette, reverse = reverse)

  if (discrete) {
    discrete_scale("fill", paste0("MountSinai_", palette), palette = pal, ...)
  } else {
    scale_fill_gradientn(colours = pal(256), ...)
  }
}

# Use in ggplot 
  # scale_color_MountSinai("main")

```


```{r Global Functions, echo = FALSE, warning = FALSE, message = FALSE}

'%!in%' <- function(x,y)!('%in%'(x,y)) # Does not include
not_all_na <- function(x) all(!is.na(x)) # Exclude columns with All NAs

```


```{r Reporting Variables, echo = FALSE, warning = FALSE, message = FALSE}

report_run_date <- Sys.Date()
# report_run_date <- "2022-08-10"
reporting_week <- floor_date(as.Date(report_run_date, "%Y-%m-%d")-7, unit="week", week_start = 7)
reporting_week_prior <- floor_date(as.Date(report_run_date, "%Y-%m-%d")-14, unit="week", week_start = 7)
reporting_week_next <- floor_date(as.Date(report_run_date, "%Y-%m-%d"), unit="week", week_start = 7)

reporting_year <- format(as.Date(report_run_date), "%Y")
reporting_month <- format(as.Date(report_run_date), "%b")
reporting_monthNum <- format(as.Date(report_run_date), "%m")


```



```{r Referrals Data Importing, echo = FALSE, warning = FALSE, message = FALSE}

# Connect to Database ----------------------------------------------------------
# conn1 <- odbcConnect("Caboodle") # Connect to Server

conn1 <- dbPool(drv = odbc(), dsn = "Caboodle", timeout = 30)

# Import Referrals+Visit Data --------------------------------------------------
referrals_conn <- tbl(conn1, "Referrals")
referrals_raw <- referrals_conn %>%
  mutate(StartInstant = as.Date(StartInstant)) %>%
  filter(StartInstant >= as.Date("2022-04-01") & StartInstant <= report_run_date) %>%
  filter(Status != "Canceled") %>%
  collect()

# Import Referrals Data for Addtional Referral Details -------------------------
# referralFactAll <- sqlQuery(conn1, "SELECT TOP 10* FROM PRDREPORT.FullAccess.ReferralFact")
referralFact_conn <- tbl(conn1, "ReferralFact")

referralFact_raw <- referralFact_conn %>%
  # head(1000) %>%
  # collect()
  mutate(StartInstant = as.Date(StartInstant)) %>%
  filter(StartInstant >= as.Date("2022-04-01") & StartInstant <= report_run_date) %>%
  group_by(ReferralKey, ReferredToDepartmentSpecialty, StartInstant, `_CreationInstant`, `_LastUpdatedInstant`, LastEnteredWorkqueueDateKey_X,
           LastEnteredWorkqueueTimeKey_X, LastEnteredWorkqueueName_X,
           Class, Priority, Redirected, Rejected, TriageRejectionReason, InAnyWorkqueue, StatusReason, SchedulingStatus,
           FirstCallMadeInstant, FirstEncounterCreatedInstant, FirstEncounterInstant, ExpirationInstant,
           WasPatientContactedWithin12Hours_X,
           ProfessionalChargeAmount, ProfessionalChargeEstimate, HospitalChargeEstimate) %>%
  summarise(total = n()) %>%
  collect()

referralFact_raw$total <- NULL

# referralFact_all <- referralFact_conn %>%
#   mutate(StartInstant = as.Date(StartInstant)) %>%
#   filter(StartInstant == as.Date("2022-11-03")) %>%
#   collect()

visitFact_conn <- tbl(conn1, "VisitFact")
visitFact_raw <- visitFact_conn %>%
  filter(ReferralKey >0) %>%
  group_by(ReferralKey, AppointmentStatus, AppointmentCreationDateKey, AppointmentCancellationDateKey) %>%
  summarise(total = n()) %>%
  collect() %>%
  group_by(ReferralKey) %>%
  mutate(first_appt = as.Date(as.character(min(AppointmentCreationDateKey)),  format = "%Y%m%d"))

# Append Additional Referral Columns -------------------------------------------
referrals_merged <- left_join(referrals_raw, subset(referralFact_raw, select = -c(StartInstant, Priority)))
referrals_merged <- referrals_merged %>%
  mutate(SentByDepID = as.character(SentByDepID),
         ReceivedByDepID = as.character(ReceivedByDepID))

```


```{r Referrals Data Processing, echo = FALSE, warning = FALSE, message = FALSE}

# Referrals Raw Data Processing ------------------------------------------------
# Priority Groups =============================================================
referrals_merged <- referrals_merged %>%
  mutate(createdWeek = floor_date(as.Date(StartInstant, "%Y-%m-%d"), unit="week", week_start = 7),
         createdYear = format(as.Date(StartInstant, "%Y-%m-%d"),"%Y"),
         createdMonNum = as.numeric(format(as.Date(StartInstant, "%Y-%m-%d"),"%m")),
         createdMonth = format(as.Date(StartInstant, "%Y-%m-%d"),"%B"),
         createdMonthYear = format(as.Date(StartInstant, "%Y-%m-%d"),"%m-%Y")) %>%
  mutate(priority_type = case_when(str_detect(toupper(Priority), "CONVENIENCE") ~ "Patient Convenience"
                                   ,str_detect(toupper(Priority), "2 DAYS") ~ "Within 2 Days"
                                   ,str_detect(toupper(Priority), "1 WEEK") ~ "Within 1 Week"
                                   ,str_detect(toupper(Priority), "2 WEEKS") ~ "Within 2 Weeks"
                                   ,str_detect(toupper(Priority), "3-6 Days") ~ "Within 1 Week" # Question: Should this be a separate category?
                                   ,str_detect(toupper(Priority), "7-14 Days") ~ "Within 2 Weeks"
                                   ,Priority == "Routine" ~ "Routine"
                                   ,TRUE ~ "Not Specified"))

```


```{r Unique Referral Volume Data, echo = FALSE, warning = FALSE, message = FALSE}

# Unique Referrals by Appointment Status -------------------------------------------------------
referrals_processed <- referrals_merged %>%
  group_by(ReferralKey) %>%
  mutate(ApptStatusFinal = NA) %>%
  mutate(ApptStatusFinal = case_when((is.na(ApptStatusFinal) & any(AppointmentStatus %in% c("Arrived","Completed"))) ~ "Arrived"
                                     ,(is.na(ApptStatusFinal) & any(AppointmentStatus %in% c("No Show", "Left without seen"))) ~ "No Show"
                                     ,(is.na(ApptStatusFinal) & any(AppointmentStatus == "Canceled")) ~ "Canceled"
                                     ,(is.na(ApptStatusFinal) & any(AppointmentStatus %in% c("Scheduled","Confirmed"))) ~ "Scheduled"
                                     ,TRUE ~ "Pending"))


# Unique Referral Volume by Appointment Status -------------------------------------------------
referral_vol <- referrals_processed %>%
  group_by(SentBySite, SentByDepID, SentByDept, SentBySpecialty,
           ReceivedBySite, ReceivedByDepID, ReceivedByDept, ReceivedBySpecialty, ReferredToDepartmentSpecialty,
           StartInstant, createdYear, createdMonthYear, createdMonNum, createdMonth, createdWeek, ReferralKey, ReferralEpicId, priority_type, ApptStatusFinal,
           Class, WasPatientContactedWithin12Hours_X, CreationToFirstEncounterDate, ExpirationInstant,
           ProfessionalChargeEstimate, HospitalChargeEstimate, Redirected, Rejected, TriageRejectionReason, InAnyWorkqueue,
           Patient_MRN, ICD_10_Chosen,
           Status, CloseReason, SchedulingStatus) %>%
  summarise(total = n()) %>%
  mutate(SentBySpecialty = case_when(SentByDept %in% c("MS EPICCARE LINK","MS RYAN CENTER LINK") ~ "ECL"
                                # ,str_detect(toupper(SentByDept), "EMERGENCY") ~ "ED"
                                # ,SentByDept == "EMERGENCY DEPARTMENT PSYCH" ~ "ED Psych"
                                # ,SentByDept == "CPEP PSYCH ED BI" ~ "ED Psych"
                                , TRUE ~ SentBySpecialty)) %>%
  mutate(SentBySite = case_when(SentByDept %in% c("MS RYAN CENTER LINK") ~ "RYAN CENTER"
                                     # ,SentByDept == "EMERGENCY DEPT BI" ~ "MSBI"
                                     # ,SentByDept == "EMERGENCY DEPT MORNINGSIDE" ~ "MSM"
                                     # ,SentByDept == "EMERGENCY DEPT WEST" ~ "MSW"
                                     # ,SentByDept == "EMERGENCY DEPARTMENT" ~ "MSH"
                                     # ,SentByDept == "EMERGENCY DEPT QUEENS" ~ "MSQ"
                                     # ,SentByDept == "EMERGENCY DEPT BI BROOKLYN" ~ "MSB"
                                     # ,SentByDept == "EMERGENCY DEPARTMENT PSYCH" ~ "MSH"
                                     # ,SentByDept == "CPEP PSYCH ED BI" ~ "MSBI"
                                     ,TRUE ~ SentBySite))

referral_vol$referral_age <- difftime(report_run_date, as.Date(referral_vol$StartInstant, "%Y-%m%-%d"), units = "days")


# Merge Appointment Scheduled Date 
referral_vol$first_appt_created <- visitFact_raw$first_appt[match(referral_vol$ReferralKey, visitFact_raw$ReferralKey)]
referral_vol <- referral_vol %>%
  mutate(scheduledWeek = floor_date(as.Date(first_appt_created, "%Y-%m-%d"), unit="week", week_start = 7),
         scheduledYear = format(as.Date(first_appt_created, "%Y-%m-%d"),"%Y"),
         scheduledMonNum = as.numeric(format(as.Date(first_appt_created, "%Y-%m-%d"),"%m")),
         scheduledMonth = format(as.Date(first_appt_created, "%Y-%m-%d"),"%B"),
         scheduledMonthYear = format(as.Date(first_appt_created, "%Y-%m-%d"),"%m-%Y"),
         scheduledYearMonth = format(as.Date(first_appt_created, "%Y-%m-%d"),"%Y-%m")) %>%
  mutate(leadDays = difftime(StartInstant, first_appt_created, units = "days")) 


# saveRDS(referral_vol, "referral_vol.rds")
# referral_vol <- readRDS("referral_vol.rds")
```


```{r Referrals Data Output, echo = FALSE, warning = FALSE, message = FALSE}

path <- "/nfs/data/Applications/Ambulatory/Data_Updated/"
saveRDS(referral_vol, paste0(path,"referral_vol.rds"))

# rm(referral_vol)
# invisible(gc())

```


```{r Referral WQ Data Import, echo = FALSE, warning = FALSE, message = FALSE}

# Import WQ Data ---------------------------------------------------------------
# wq_history_conn <- tbl(conn1, "ReferralWorkqueueEventFactX")
# wq_reasons_conn <- tbl(conn1, "ReferralWQReasons")

```


```{r WQ Data Processing, echo = FALSE, warning = FALSE, message = FALSE}

# # Subset WQ History Data based on Referrals Data -------------------------------
# wq_history_merged <- left_join(referral_vol[,c("ReferralKey", "ReferralEpicId", "Status", "SchedulingStatus", "InAnyWorkqueue", "priority_type")], 
#                                test <- wq_history_conn %>% 
#                                  filter(ReferralKey >= 0) %>%
#                                  # filter(ReferralType %in% c("TO","FROM")) %>% # Remove unspecified wq types 
#                                  filter(`_CreationInstant` >= as.Date("2022-04-01")) %>%
#                                  collect())
# 
# wq_history_merged <- wq_history_merged %>% # Filter WQ History based on Referral IDs found in Referrals table
#   filter(ReferralKey %in% unique(referral_vol$ReferralKey))
# 
# wq_history_merged <- wq_history_merged %>% 
#   filter(!is.na(EventDateKey)) %>%
#   mutate(EventDate = as.Date(lubridate::ymd(EventDateKey)),
#          EventTime = paste0(" ",sub('(\\d{2})$', ':\\1', EventTimeKey)),
#          EventTime = gsub(" :", "00:", EventTime),
#          EventTime = gsub(" ","",EventTime),
#          releaseDate = as.Date(lubridate::ymd(ReleaseDateKey))) %>%
#   mutate(EventDateTime = as.POSIXct(paste(EventDate, EventTime), format="%Y-%m-%d %H:%M"))
# 
# # wq_history_merged$releaseDate <- case_when(is.na(wq_history_merged$releaseDate) ~ Sys.Date(),
# #                                            TRUE ~ wq_history_merged$releaseDate) 
# 
# 
# wq_history_merged <- wq_history_merged %>%
#   arrange(EventDateTime, releaseDate) %>%
#   arrange(ReferralKey) %>%
#   group_by(ReferralKey, EpicWorkqueueId, releaseDate) %>%
#   mutate(ID = seq_len(n())) %>%
#   mutate(wq_entered = min(EventDateTime),
#          wq_exited = max(releaseDate),
#          wq_latest_reason = case_when(EventDateTime == wq_entered & releaseDate == wq_exited ~ ReferralWorkqueueReason,
#                                       TRUE ~ ""))
# 
# 
# # Unique WQ Volume Data with WQ Entered and Existed Times
# wq_volume_data <- wq_history_merged %>%
#   filter(wq_latest_reason != "") %>%
#   group_by(ReferralKey, ReferralEpicId, InAnyWorkqueue, ReferralType, EpicWorkqueueId, wq_entered, wq_exited, wq_latest_reason) %>%
#   summarise(referral_type = n()) %>%
#   mutate(wq_entered = format(as.Date(wq_entered, "%Y-%m-%d %HH:%MM:%SS"),"%Y-%m-%d %HH:%MM:%SS"),
#          wq_enteredWeek = floor_date(as.Date(wq_entered, "%Y-%m-%d %HH:%MM:%SS"), unit="week", week_start = 7),
#          wq_enteredYear = format(as.Date(wq_entered, "%Y-%m-%d %HH:%MM:%SS"),"%Y"),
#          wq_enteredMonNum = as.numeric(format(as.Date(wq_entered, "%Y-%m-%d %HH:%MM:%SS"),"%m")),
#          wq_enteredMonth = format(as.Date(wq_entered, "%Y-%m-%d %HH:%MM:%SS"),"%B"),
#          wq_enteredMonthYear = format(as.Date(wq_entered, "%Y-%m-%d %HH:%MM:%SS"),"%m-%Y"),
#          wq_enteredDay = format(as.Date(wq_entered, "%Y-%m-%d %HH:%MM:%SS"),"%A")) %>%
#   mutate(wq_exitedWeek = floor_date(as.Date(wq_exited, "%Y-%m-%d"), unit="week", week_start = 7),
#          wq_exitedYear = format(as.Date(wq_exited, "%Y-%m-%d"),"%Y"),
#          wq_exitedMonNum = as.numeric(format(as.Date(wq_exited, "%Y-%m-%d"),"%m")),
#          wq_exitedMonth = format(as.Date(wq_exited, "%Y-%m-%d"),"%B"),
#          wq_exitedMonthYear = format(as.Date(wq_exited, "%Y-%m-%d"),"%m-%Y"),
#          wq_exitedDay = format(as.Date(wq_exited, "%Y-%m-%d"),"%A")) %>%
#   mutate(wq_latest_reason = toupper(wq_latest_reason)) %>%
#   mutate(reason_type = case_when(ReferralType == "FROM" & str_detect(wq_latest_reason, "DEACTIVATED OR INVALID|NO DEPT|WTC NEED") ~ "Missing department",
#                                  ReferralType == "FROM" & str_detect(wq_latest_reason, "OUTGOING") ~ "Outgoing Referral needs scheduling",
#                                  ReferralType == "FROM" & str_detect(wq_latest_reason, "TRIAGE") ~ "Triage rejected",
#                                  ReferralType == "FROM" & str_detect(wq_latest_reason, "PSYCH") ~ "Psych referrals",
#                                  ReferralType == "TO" & str_detect(wq_latest_reason, "NEEDS SCHEDULING|NEEDS TO BE WORKED|INCOMING REFERRAL NEEDS AUTH") 
#                                  ~ "Both scheduling and authorization outstanding",
#                                  ReferralType == "TO" & str_detect(wq_latest_reason, "AUTHORIZED AND NEED SCHEDULING|NEED SCHEDULING") ~ "Authorized but scheduling needed",
#                                  ReferralType == "TO" & str_detect(wq_latest_reason, "NEED AUTHORIZATION|NO AUTHORIZATION|INVALID AUTH NUMBER") ~ "Authorization needed",
#                                  ReferralType == "TO" & str_detect(wq_latest_reason, "UNABLE TO CONTACT") ~ "Unable to Contact Patient",
#                                  ReferralType == "TO" & str_detect(wq_latest_reason, " RFL INVALID AUTH NUMBER|W/O LINKED REFERRAL") ~ "Scheduled but Authorization is outstanding",
#                                  TRUE ~ "Other"
#                                  ))
# wq_volume_data$wq_entered <- format(as.Date(wq_volume_data$wq_entered, "%Y-%m-%d %HH:%MM:%SS"),"%Y-%m-%d")
# wq_volume_data$referral_age <- difftime(wq_volume_data$wq_exited, as.Date(wq_volume_data$wq_entered, "%Y-%m-%d"), units = "days")

# wq_volume_data$ wq_enteredDay <- format(as.Date(wq_volume_data$wq_entered, "%Y-%m-%d %HH:%MM:%SS"),"%A")
# wq_volume_data$wq_exitedDay = format(as.Date(wq_volume_data$wq_exited, "%Y-%m-%d"),"%A")
# wq_volume_data$wq_entered <- format(as.Date(wq_volume_data$wq_entered, "%Y-%m-%d %HH:%MM:%SS"),"%Y-%m-%d")
  
```


```{r Workqueue History Data Output, echo = FALSE, warning = FALSE, message = FALSE}

# path <- "/nfs/data/Applications/Ambulatory/Data_Updated/"
# saveRDS(wq_volume_data, paste0(path,"wq_volume_data.rds"))

# rm(wq_volume_data)
# invisible(gc())

```


```{r WQ Reasons Processing, echo = FALSE, warning = FALSE, message = FALSE}

# wq_reasons_raw <- wq_reasons_conn %>%
#   collect() %>%
#   mutate(wq_type = case_when(str_detect(WorkqueueName, " TO ") ~ "TO",
#                              str_detect(WorkqueueName, " FROM ") ~ "FROM",
#                              str_detect(WorkqueueName, "TRIAGE") ~ "TRIAGE",
#                              str_detect(WorkqueueName, "AUTHORIZATION REQUIRED") ~ "AUTHORIZATION",
#                              str_detect(WorkqueueName, "PAS") ~ "PAS",
#                              TRUE ~ ""))
# 
# wq_reasons_raw <- wq_reasons_raw %>%
#   filter(ReferralEpicId %in% unique(referral_vol$ReferralEpicId)) # Filter Current WQs by Referrals Found in Referrals Table
# 
# 
# ## WQ Reasons Grouping ---------------------------------------------------------
# wq_reasons_raw <- wq_reasons_raw %>%
#   mutate(ReferralWorkqueueReason = toupper(ReferralWorkqueueReason)) %>%
#   mutate(reason_type = case_when(wq_type == "FROM" & str_detect(ReferralWorkqueueReason, "DEACTIVATED OR INVALID|NO DEPT|WTC NEED") ~ "Missing Department",
#                                  wq_type == "FROM" & str_detect(ReferralWorkqueueReason, "OUTGOING") ~ "Outgoing Referral Needs Scheduling",
#                                  wq_type == "FROM" & str_detect(ReferralWorkqueueReason, "TRIAGE") ~ "Triage Rejected",
#                                  wq_type == "FROM" & str_detect(ReferralWorkqueueReason, "PSYCH") ~ "Psych Referrals",
#                                  wq_type == "TO" & str_detect(ReferralWorkqueueReason, "AUTHORIZED AND NEED SCHEDULING|NEED SCHEDULING") ~ "Authorized but Scheduling Needed",
#                                  wq_type == "TO" & str_detect(ReferralWorkqueueReason, "NEED AUTHORIZATION|NO AUTHORIZATION") ~ "Authorization Needed",
#                                  wq_type == "TO" & str_detect(ReferralWorkqueueReason, "UNABLE TO CONTACT") ~ "Unable to Contact Patient",
#                                  TRUE ~ "Other"
#                                  )) %>%
#   mutate(creation_date = as.Date(lubridate::ymd(CreationDateKey)),
#          entry_date = as.Date(lubridate::ymd(EntryDateKey))) %>%
#   mutate(days_since_creation = difftime(Sys.Date(), creation_date, units = "days"),
#          days_wq = difftime(Sys.Date(), entry_date, units = "days"))
# 
# 
# wq_reasons_raw$priority_type <- referral_vol$priority_type[match(wq_reasons_raw$ReferralEpicId, referral_vol$ReferralEpicId)]
# wq_reasons_raw$WasPatientContactedWithin12Hours_X <- referral_vol$WasPatientContactedWithin12Hours_X[match(wq_reasons_raw$ReferralEpicId, referral_vol$ReferralEpicId)]
# 
# 
# # library(plyr)
# # duplicated_rows <- ddply(wq_reasons_raw,.(ReferralEpicId),nrow)
# 
# wq_reasons_raw <- wq_reasons_raw %>%
#   distinct()

```


```{r Workqueue Reasons Data Output, echo = FALSE, warning = FALSE, message = FALSE}

# path <- "/nfs/data/Applications/Ambulatory/Data_Updated/"
# saveRDS(wq_reasons_raw, paste0(path,"wq_reasons_data.rds"))

```

